---
title: "small_OF_stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load small open field measures data

```{r}

# df = read.csv("D:/Users/BClarkLab/github/Berkowitz_et_al_2021/GrossLocomotion/gross_locomotion.csv")
df = read.csv('/Users/lauraberkowitz/github/TgF344-AD_Open_Field/notebooks/data/small_open_field_measures.csv')
df$subID<- factor(df$subID)
df$group <- factor(df$group)
df$time_point <- factor(df$time_point)
df$day<- factor(df$day)

# remove rats with missing data 
df <- df[complete.cases(df), ]

summary(df)


```

## Examine 2x3x3 mixed model for locomotion measures 
```{r}
library(olsrr)
df$path_length_trans <- sqrt(df$path_length)

mdl <- lm(path_length_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)

```
## remove day as its not a great predictor of path length
```{r}
mdl <- lm(path_length_trans ~ (group + time_point)^2, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl)

summary(mdl)

```

## Examine Thigmotaxis
```{r}
library(olsrr)
df$thigmotaxis_trans <- (df$thigmotaxis)^3.5

mdl <- lm(thigmotaxis_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

## remove day as its not a great predictor of Thigmotaxis
```{r}
mdl <- lm(thigmotaxis_trans ~ (group + time_point)^2, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl)

summary(mdl)
coef(mdl)

cell.means <- aggregate(x=list(Y=df$thigmotaxis),
                        by=list(B=df$time_point),
                        FUN=mean)

print(cell.means/600)
```

## Examine median velocity
```{r}
library(olsrr)
df$velocity_trans <- log10(df$median_velocity)

mdl <- lm(velocity_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

## remove day as its not a great predictor of median velocity
```{r}
mdl <- lm(velocity_trans ~ (group + time_point)^2, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl)

summary(mdl)

```

```{r}
library(olsrr)
df$searcharea_trans <- (df$search_area)

mdl <- lm(searcharea_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

## remove day as its not a great predictor of median velocity
```{r}
mdl <- lm(searcharea_trans ~ (group + time_point)^2, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl)

summary(mdl)

```

## Lets look at stopping behavior
```{r}
library(olsrr)
df$n_stops_trans <- sqrt(df$n_stops)

mdl <- lm(n_stops_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

```{r}
mdl_full <- lm(n_stops_trans ~ group*day, data = df,contrasts = c(group=contr.helmert,day=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(n_stops_trans ~ group + day, data = df,contrasts = c(group=contr.helmert,day=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)

summary(mdl_red)


```

## Stop duration
```{r}
library(olsrr)
df$median_stop_duration_trans <- log(df$median_stop_duration)

mdl <- lm(median_stop_duration_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

```{r}
mdl_full <- lm(median_stop_duration_trans ~ group*time_point, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(median_stop_duration_trans ~ group + time_point, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)


summary(mdl_red)

```

## Stop intervals
```{r}
library(olsrr)
df$median_inter_stop_trans <- log(df$median_inter_stop_interval)

mdl <- lm(median_inter_stop_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

```{r}
mdl_full <- lm(median_inter_stop_trans ~ group*time_point, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(median_inter_stop_trans ~ group + time_point, data = df,contrasts = c(group=contr.helmert,time_point=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)


summary(mdl_red)

```

## Home Base evaluation
```{r}
library(olsrr)
df$hb_dist_to_wall_trans <- (df$hb_dist_to_wall)

mdl <- lm(hb_dist_to_wall_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

```{r}
mdl_full <- lm(hb_dist_to_wall_trans ~ group*time_point, data = df,contrasts = c(group=contr.sum,time_point=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(hb_dist_to_wall_trans ~ group + time_point, data = df,contrasts = c(group=contr.sum,time_point=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)

summary(mdl_red)

```

```{r}
# mean distance of HB from boundary by group and day 
library(dplyr)
df %>%                                        # Specify data frame
  group_by(group) %>%                         # Specify group indicator
  summarise_at(vars(hb_dist_to_wall),              # Specify column
               list(name = std)               # Specify function




```

```{r}
library(olsrr)
df$time2hb_trans <- (df$time2hb)

mdl <- lm(time2hb_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```
```{r}
mdl_full <- lm(time2hb_trans ~ group*time_point, data = df,contrasts = c(group=contr.sum,time_point=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(time2hb_trans ~ group + time_point, data = df,contrasts = c(group=contr.sum,time_point=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)

summary(mdl_red)
```

```{r}
# mean distance of HB from boundary by group and day 
df %>%                                        # Specify data frame
  group_by(time_point) %>%                         # Specify group indicator
  summarise_at(vars(time2hb),              # Specify column
               list(name = mean))               # Specify function




```

```{r}
library(olsrr)
df$time_in_hb_trans <- log2(df$time_in_homebase)

mdl <- lm(time_in_hb_trans ~ (group + day + time_point)^2, data = df)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

```{r}
mdl_full <- lm(time_in_hb_trans ~ group*day, data = df,contrasts = c(group=contr.sum,day=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(time_in_hb_trans ~ group + day, data = df,contrasts = c(group=contr.sum,day=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)

summary(mdl_red)
```

```{r}
# mean distance of HB from boundary by group and day 
df %>%                                        # Specify data frame
  group_by(group) %>%                         # Specify group indicator
  summarise_at(vars(time_in_homebase),              # Specify column
               list(name = mean))               # Specify function




```


```{r}

# df = read.csv("D:/Users/BClarkLab/github/Berkowitz_et_al_2021/GrossLocomotion/gross_locomotion.csv")
df_hb_dist = read.csv('/Users/lauraberkowitz/github/TgF344-AD_Open_Field/notebooks/data/primary_hb_dist_table.csv')
df_hb_dist$subID<- factor(df_hb_dist$rat)
df_hb_dist$group <- factor(df_hb_dist$group)
df_hb_dist$time_point <- factor(df_hb_dist$time_point)

# remove rats with missing data 
df_hb_dist <- df_hb_dist[complete.cases(df_hb_dist), ]

summary(df_hb_dist)


```

```{r}
library(olsrr)
df_hb_dist$mean_hb_distance_over_days_trans <- (df_hb_dist$mean_hb_distance_over_days)^1.5

mdl <- lm(mean_hb_distance_over_days_trans ~ (group + time_point)^2, data = df_hb_dist)
lm_diag_plots(mdl)
ols_step_all_possible(mdl)
```

```{r}
mdl_full <- lm(mean_hb_distance_over_days_trans ~ group*time_point, data = df_hb_dist,contrasts = c(group=contr.sum,time_point=contr.helmert))
lm_diag_plots(mdl_full)

mdl_red <- lm(mean_hb_distance_over_days_trans ~ group + time_point, data = df_hb_dist,contrasts = c(group=contr.sum,time_point=contr.helmert))
lm_diag_plots(mdl_red)

anova(mdl_full,mdl_red)

summary(mdl_full)
```

```{r}
# mean distance of HB from boundary by group and day 
df_hb_dist %>%                                        # Specify data frame
  group_by(group,time_point) %>%                         # Specify group indicator
  summarise_at(vars(mean_hb_distance_over_days),              # Specify column
               list(name = median))               # Specify function

```
